# Install libraries

```{r}
install.packages("bupaverse")
install.packages("bpmnVisualizationR")
```

# Analyse du flux de contrôle

```{r}
# Compute frequency
library(bupaR)
library(dplyr)

# Import the CSV process execution data and create a data frame
df <- read.csv("data/loan-app-process-data-simulated.csv")
print(df)
```

## Create bupaR activity log data structure

```{r}
# Create bupaR activity log data structure
process_data <- df %>%
  dplyr::rename(start = startTime,
                 complete = completeTime) %>%
  convert_timestamps(columns = c("start", "complete"), format = ymd_hms) %>%
  mutate(Actor = NA) %>%
  activitylog(case_id = "loanID",
              activity_id = "activity",
              resource_id = "Actor",
              timestamps = c("start", "complete"))

print(process_data)
```

## Getting basic summary

```{r}
# getting basic summary
process_data %>% n_activities
process_data %>% n_activity_instances
process_data %>% n_cases
```

## Explore executed process instances

```{r}
process_data %>% trace_explorer(coverage = 1)
```

## Compute frequency

```{r}
# get frequency of activities
process_data %>% activities
```

# Analyse de la Performance

```{r}
process_data %>% processing_time("case", units = "hours")%>%
  plot()
```

```{r}
process_data %>% 
  process_matrix(performance(FUN = mean, units = "hours", flow_time = "idle")) %>%
  plot()
```

```{r}
library(psmineR)
process_data %>%
  ps_detailed(segment_coverage = 0) %>%
  plot()

```

# Animate data

```{r}
library(processanimateR)

event_log <- to_eventlog(process_data)

animate_process(event_log)

animate_process(event_log, mapping = token_aes(color = token_scale("red")))
```

# Prediction

## Prepare the dataset

```{r}
library("processpredictR")

process_data_for_prediction <- prepare_examples(process_data, task = "outcome")

print(process_data_for_prediction)
```

## Split into training/testing data

```{r}
split <- process_data_for_prediction %>% split_train_test(split = 0.8)
split
```

## Create the predictive model

```{r}
library(tensorflow)
library(keras)

model <- split$train_df %>% create_model(name = "my_first_outcome_predictive_model")

# the preprocessing steps, such as tokenizing of sequences, normalizing numerical features, etc. happen within the create_model() function and are abstracted from the user.
```

## Model Compilation & Training

```{r}
model %>% compile() # model compilation
```

```{r}
hist <- fit(object = model, train_data = split$train_df, epochs = 5)
```

```{r}
hist$metrics
```

## Make predictions on the test data

```{r}
predictions <- model %>% predict(test_data = split$test_df, 
                                 output = "append") # default
predictions %>% head(5)
```

```{r}
# print confusion matrix
confusion_matrix(predictions)
```

```{r}
model %>% evaluate(split$test_df)
```

```{r}
# library(reticulate)
# use_python("C:\\Users\\noura\\AppData\\Local\\Programs\\Python\\Python310")
```
